Stats

### 2022-08-15 paper/manuscript.Rmd
correct data exclusion for retest hedge

```{r setup, include = FALSE}
library("papaja")
library("ggplot2")
library("ggpubr")
theme_set(theme_classic())
```

@@

```{r load_data}
library(tidyverse)
library(brms)
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised). The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`). Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position). We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.

@@

## Results
(ref:figlab2) **Measuring inter-individual variation**. 
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small points show the mean performance for each subject. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection. Color of data points denotes age group.

@@

[^fn2]: In the hedge version, we excluded one 5-year-old child from the test-retest analysis. The performance of the mentioned child was 3 standard deviations above the mean on both test days. Including the child yielded a *Pearson* correlation coefficient of *r* = 0.87.

@@

# Supplements
## Child sample
### Webcam coding
(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**. 
Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level.

@@

```{r webcam_table, results = "asis"}
# webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
#   mutate(across(c(WAIC, SE_WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>% 
#   mutate_if(is.numeric, round, 2)
#     
# papaja::apa_table(
#   webcam_models, 
#   caption = "Model comparison for exploratory webcam coding of parental interference", 
#   note = "All models included random intercepts for participant and target position.", 
#   escape = T
# )
```

>>>>

```{r setup, include = FALSE}
library("papaja")
library("ggplot2")
library("ggpubr")
library("tidyverse")
library("brms")
theme_set(theme_classic())
```

@@

```{r load_data}
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised). The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`). Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position). We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.

@@

## Results
(ref:figlab2) **Measuring inter-individual variation**. 
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*.
Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small points show the mean performance for each subject averaged across trials. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection. Color of data points denotes age group.

@@

```{r hedge_retest_correlationcoefficients}
hedge_retest_correlationcoefficients <- readRDS(file = "../saves/gafo-hedge-retest-correlationcoefficients.rds")
```

[^fn2]: In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis. The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample. Including the two children yielded a *Pearson* correlation coefficient of *r* = `r hedge_retest_correlationcoefficients$pearson_retest[hedge_retest_correlationcoefficients$sample == "kids" & hedge_retest_correlationcoefficients$analysis == "outlier included"]`. Including the two adults yielded a *Pearson* correlation coefficient of *r* = `r hedge_retest_correlationcoefficients$pearson_retest[hedge_retest_correlationcoefficients$sample == "adults" & hedge_retest_correlationcoefficients$analysis == "outlier included"]`.

@@

# Supplements
## Child sample
### Webcam coding
(ref:figlab4) **Model comparison for exploratory webcam coding of parental interference**. 
Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level (i.e., average across trials per subject).

@@

```{r webcam_table, results = "asis"}
webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD, SE), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

papaja::apa_table(
  webcam_models,
  caption = "Model comparison for exploratory webcam coding of parental interference",
  note = "All models included random intercepts for participant and target position.",
  escape = T
)
```

### 2022-08-15 paper/manuscript.tex
correct data exclusion for retest hedge

To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance by age (in months, z-transformed) and data collection mode (reference category: in-person supervised). The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}). Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position). We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.

@@

\caption{\textbf{Measuring inter-individual variation}.
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
Small points show the mean performance for each subject. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection. Color of data points denotes age group.}\label{fig:fig2}
\end{figure}

@@

For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 5-year-old child from the test-retest analysis. The performance of the mentioned child was 3 standard deviations above the mean on both test days. Including the child yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.87.}

@@

\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}.
Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level.}\label{fig:fig4}
\end{figure}

@@

>>>>

To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised). The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}). Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position). We expected that trials could differ in their difficulty depending on the target centrality and that these these item effects could vary between participants.

@@

\caption{\textbf{Measuring inter-individual variation}.
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
Small points show the mean performance for each subject averaged across trials. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection. Color of data points denotes age group.}\label{fig:fig2}
\end{figure}

@@

For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis. The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample. Including the two children yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.89. Including the two adults yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.73.}

@@

\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}.
Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig4}
\end{figure}

@@

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}

\begin{tabular}{lllll}
\toprule
Predictor & \multicolumn{1}{c}{WAIC} & \multicolumn{1}{c}{Weight} & \multicolumn{1}{c}{ELPD} & \multicolumn{1}{c}{SE}\\
\midrule
By trial - \# Verification choice & 262.98 & 0.57 & 0.00 & 0.00\\
By trial - Null model & 263.25 & 0.43 & -0.13 & 1.19\\
By trial - Parental interference index & 264.32 & 0.00 & -0.67 & 0.97\\
By trial - \# Repeated testquestion & 265.34 & 0.00 & -1.18 & 1.26\\
By trial - \# Words uttered by caregiver & 266.27 & 0.00 & -1.65 & 1.21\\
By trial - \# Hints eyes & 266.33 & 0.00 & -1.68 & 1.27\\
By subject - \# Repeated testquestion & 83.83 & 0.70 & 0.00 & 0.00\\
By subject - Parental interference index & 88.50 & 0.00 & -2.34 & 3.56\\
By subject - Null model & 89.62 & 0.00 & -2.90 & 3.60\\
By subject - \# Verification choice & 89.75 & 0.30 & -2.96 & 4.46\\
By subject - \# Words uttered by caregiver & 90.46 & 0.00 & -3.32 & 4.21\\
By subject - \# Hints eyes & 92.90 & 0.00 & -4.54 & 3.73\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

### 2022-08-15 stats/analysis.Rmd
correct data exclusion for retest hedge

```{r retest_hedge_exclude_outliers}
# exclude outliers
hedge_retest <- hedge_retest %>%
  filter(mean_reliday1 < mean(mean_reliday1) + 3*sd(mean_reliday1), mean_reliday1 > mean(mean_reliday1) - 3*sd(mean_reliday1),
         mean_reliday2 < mean(mean_reliday2) + 3*sd(mean_reliday2), mean_reliday2 > mean(mean_reliday2) - 3*sd(mean_reliday2))
```

>>>>

```{r retest_hedge_exclude_outliers}
# exclude outliers
hedge_retest_all <- hedge_retest

hedge_retest <- hedge_retest_all %>%
  group_by(sample) %>%
  filter(mean_reliday1 <= mean(mean_reliday1) + 3*sd(mean_reliday1),
         mean_reliday1 >= mean(mean_reliday1) - 3*sd(mean_reliday1),
         mean_reliday2 <= mean(mean_reliday2) + 3*sd(mean_reliday2), 
         mean_reliday2 >= mean(mean_reliday2) - 3*sd(mean_reliday2))

# see how subject exclusion influences the retest correlation
hedge_retest_correlationcoefficients <- rbind(
  (hedge_retest %>%
  group_by(sample) %>%
  summarise(
    n = n_distinct(subjID),
    pearson_retest = cor(mean_reliday1, mean_reliday2, method = "pearson") %>% round(2), 
    analysis = "outlier excluded",
  )), 
  (hedge_retest_all %>%
  group_by(sample) %>%
  summarise(
    n = n_distinct(subjID),
    pearson_retest = cor(mean_reliday1, mean_reliday2, method = "pearson") %>% round(2), 
    analysis = "outlier included",
  )))

hedge_retest_correlationcoefficients

saveRDS(hedge_retest_correlationcoefficients, file = "../saves/gafo-hedge-retest-correlationcoefficients.rds")
```
